\documentclass[10pt, a4paper]{article}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{enumerate}
\usepackage{caption, subcaption, floatrow, subfig}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{xfrac}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usetikzlibrary{plotmarks, calc}
\usepackage{standalone}
\usepackage{url}

%%%%%%% COLORS
\usepackage{xcolor, colortbl}
\newcolumntype{S}{>{\columncolor{lime!50}}c}         % serial small
\newcolumntype{L}{>{\columncolor{cyan!50}}c}         % serial large
\newcolumntype{P}{>{\columncolor{red!50}}c}          % parallel& 
%%%%%%%

\newcommand{\reals}{\mathbb{R}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\semi}[1]{\lvert#1\rvert}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\inner}[2]{\ensuremath{\left(#1, #2\right)}}
\renewcommand{\brack}[1]{\langle#1\rangle}
\newcommand{\average}[1]{\ensuremath{\langle#1\rangle} }
\newcommand{\jump}[1]{\ensuremath{[\![#1]\!]} }
\newcommand{\mat}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\dual}[1]{\ensuremath{{#1}^{\prime}}}
\renewcommand{\vec}[1]{\mat{#1}}
\newcommand{\supp}{\operatorname{supp}} 

\oddsidemargin=3pt
\textwidth=500pt
\topmargin=3pt

\title{Efficiency of Q-cap and W-cap preconditioners}

\begin{document}
\maketitle

\section*{Introduction}
This note collects new results that address comments of the reviewers on our paper. 
The comments boil down to the following four points: (i) The computational results 
presented are four rather small problems. (ii) The results are missing cost evaluation. 
(iii) It would be nice to compare the proposed preconditioners with some existing 
alternatives. (iv) It would be nice if the eigenvalue problem of the $Q$-cap were solved
analytically (as much as possible).

\section*{Preliminaries}
The results below are for the most part obtained on a desktop PC with 16 GB of RAM 
and four Intel Core i5-2500 cpus clocking at 3.3 GHz. The small eigenvalue problems 
required for constructing the approximations of fractional Sobolev norms are solved 
with routines from LAPACK\cite{lapack} implemented in OpenBlas\cite{openblas}
and called from Julia \cite{julia}. The large eigenvalue problems that are used to 
obtain condition numbers of the $Q$, $W$-cap preconditioned systems are solved with 
routines from SLEPc\cite{slepc} - in particular,
a generalized Davidson method with Cholesky preconditioning is employed. Finally the 
implementation of algebraic multigrid (AMG) is taken from PETSc\cite{petsc}.

In the experiments we shall consider two geometrical configurations. \textit{Uniform} 
mesh refers to a unit square (2$d$ domain) coupled to a horizontal line through 
$y=\sfrac{1}{2}$ (1$d$ domain). The domain is discretized uniformly into $2N^2$ 
triangular cells and $N$ interval cells. \textit{Non-uniform} mesh has as the two 
dimensional domain a bi-unit square coupled to a $Y$-shaped bifurcation which
is the one dimensional domain. The discretization of \textit{non-uniform} mesh is 
unstructured. The \textit{non-uniform} mesh represents a less academical example.

Finally, we shall denote as $n$ the dimension of the space where the 2$d$ unknown 
is sought while $m$ is the dimension of the spaces of the 1$d$ unknown (and the 
Lagrange multiplier). Obviously $n+2m$ is the total size of the linear system to 
be solved.

\section*{Results}
Condition numbers of the $Q$-cap and $W$-cap preconditioned systems are listed in
respectively in tables \ref{tab:cond_Qcap} for \textit{uniform} and 
\ref{tab:cond_Wcap} \textit{non-uniform} mesh. In all four cases they are 
bounded. Note that in comparison to the results presented in the paper the size 
of the considered problems has grown about eight times. Also 
note that for $\epsilon \ll 1$ the condition number is close to that of the Schur 
complement preconditioner (as was true in the paper).
%Unif cond
\begin{table}[ht]
  \caption{Condition numbers of the preconditioned systems on \textit{uniform}
  meshes for different values of parameter $\epsilon$. (Top) $Q$-cap
  preconditioner. (Bottom) $W$-cap preconditioner.
}
\label{tab:cond_Qcap}
\footnotesize{
\begin{tabular}{l|ccccccc}
\hline
($n$, $m$)\textbackslash $\epsilon$ & $10^{-3}$ & $10^{-2}$ & $10^{-1}$ & $10^{0}$ & $10^{1}$ & $10^{2}$ & $10^{3}$\\
\hline
(25, 5) & 2.633 & 2.760 & 3.686 & 5.716 & 6.427 & 6.514 & 6.523\\
(81, 9) & 2.655 & 2.969 & 4.786 & 6.979 & 7.328 & 7.357 & 7.360\\
(289, 17) & 2.698 & 3.323 & 5.966 & 7.597 & 7.697 & 7.715 & 7.717\\
(1089, 33) & 2.778 & 3.905 & 7.031 & 7.882 & 7.818 & 7.816 & 7.816\\
(4225, 65) & 2.932 & 4.769 & 7.830 & 8.016 & 7.855 & 7.843 & 7.843\\
(16641, 129) & 3.217 & 5.857 & 8.343 & 8.081 & 7.868 & 7.854 & 7.852\\
(66049, 257) & 3.710 & 6.964 & 8.637 & 8.113 & 7.872 & 7.856 & 7.855\\
\hline
\hline
(25, 5) & 2.618 & 2.612 & 2.514 & 3.292 & 3.945 & 4.038 & 4.048\\
(81, 9) & 2.619 & 2.627 & 2.546 & 3.615 & 3.998 & 4.044 & 4.048\\
(289, 17) & 2.623 & 2.653 & 2.780 & 3.813 & 4.023 & 4.046 & 4.049\\
(1089, 33) & 2.631 & 2.692 & 3.194 & 3.925 & 4.036 & 4.048 & 4.049\\
(4225, 65) & 2.644 & 2.740 & 3.533 & 3.986 & 4.042 & 4.048 & 4.049\\
(16641, 129) & 2.668 & 2.788 & 3.761 & 4.017 & 4.046 & 4.049 & 4.049\\
(66049, 257) & 2.703 & 3.066 & 3.896 & 4.033 & 4.047 & 4.049 & 4.049\\
\hline
\end{tabular}
}
\end{table}

%
%Vcap cond
%Unif
\begin{table}[hb]
  \caption{Condition numbers of the preconditioned systems on \textit{non-uniform}
  meshes for different values of parameter $\epsilon$. (Top) $Q$-cap
  preconditioner. (Bottom) $W$-cap preconditioner.
}
\label{tab:cond_Wcap}
\footnotesize{
\begin{tabular}{l|ccccccc}
\hline
($n$, $m$)\textbackslash $\epsilon$ & $10^{-3}$ & $10^{-2}$ & $10^{-1}$ & $10^{0}$ & $10^{1}$ & $10^{2}$ & $10^{3}$\\
\hline
(1466, 55) & 2.773 & 3.811 & 6.401 & 7.181 & 7.205 & 7.207 & 7.208\\
(5584, 107) & 2.926 & 4.597 & 7.018 & 7.314 & 7.282 & 7.280 & 7.279\\
(21905, 212) & 3.181 & 5.453 & 7.381 & 7.365 & 7.308 & 7.304 & 7.303\\
(87260, 422) & 3.630 & 6.374 & 7.689 & 7.493 & 7.426 & 7.421 & 7.421\\
\hline
\hline
(1466, 55) & 2.637 & 2.713 & 3.385 & 3.962 & 4.040 & 4.048 & 4.049\\
(5584, 107) & 2.656 & 2.765 & 3.678 & 4.006 & 4.045 & 4.048 & 4.049\\
(21905, 212) & 2.687 & 2.896 & 3.850 & 4.028 & 4.047 & 4.049 & 4.049\\
(87260, 422) & 2.727 & 3.274 & 3.941 & 4.038 & 4.048 & 4.049 & 4.049\\
\hline
\end{tabular}
}
\end{table}

Iteration counts of the preconditioner MinRes method with $Q$, $W$-cap preconditioners 
are listed in tables \ref{tab:iter_unif}, \ref{tab:iter_nonunif}. For convergence, 
absolute error of the preconditioned residual is required to be less than $10^{-12}$. 
Note that this is stricter than in the paper. The iteration counts are nicely bounded
%Note on convergence properties
\footnote{On \textit{uniform} mesh we have also monitored the $H^1_0$ norm of the 2$d$ solution. 
For problems with less than one million dofs the error was interpolated into DG$_4$ 
space. For larger system the error was computed in the same space as the numerical 
solution. With these metrics the error decreases linearly (or better) until penultimate 
discretization where it begins to stagnate.}. Note
that as in the paper $W$-cap comes out slightly more efficient for $\epsilon\gg 1$. 
This was observed in the original results as well.

Note that the largest problems considered in this experiments outgrow those from 
the paper by approximately factor ten. These problems are such that they barely 
fit into the RAM. For even larger problems one shall therefore assemble and solve 
the systems in parallel. At the moment we only have a serial implementation of the 
trace matrix and so distributed computing is not feasible. We remark, that for 
some of the larger problems to be run in parallel, the eigenvalue problem required 
by the $Q$-cap preconditioner could still be small and easily computed on a single 
cpu. The resulting operator would then have to be broadcasted to the 
remaining processes.

The new results do not contradict those presented in the paper in any way. Moreover, 
both the eigenvalue problems and the linear systems are quite large. Altogether, 
they should make the reviewers happy. Point (i) should therefore be addressed by 
adding the new results to appropriate tables.
%Qcap iters
\begin{table}[ht]
  \caption{Iteration counts with the $Q$-cap preconditioned system (top) and $W$-cap 
  preconditioned system (bottom) for different values of parameter $\epsilon$. 
  \textit{Uniform} mesh.
}
\label{tab:iter_unif}
\footnotesize{
\begin{tabular}{l|ccccccc}
\hline
($n$, $m$)\textbackslash $\epsilon$ & $10^{-3}$ & $10^{-2}$ & $10^{-1}$ & $10^{0}$ & $10^{1}$ & $10^{2}$ & $10^{3}$\\
\hline
(66049, 257) & 20 & 34 & 37 & 32 & 28 & 24 & 21\\
(263169, 513) & 22 & 34 & 34 & 30 & 26 & 24 & 20\\
(1050625, 1025) & 24 & 33 & 32 & 28 & 26 & 22 & 18\\
(4198401, 2049) & 26 & 32 & 30 & 26 & 24 & 20 & 17\\
(8392609, 2897) & 26 & 30 & 30 & 26 & 22 & 19 & 15\\
(11068929, 3327) & 26 & 30 & 30 & 26 & 22 & 19 & 15\\
\hline
\hline
(66049, 257) & 17 & 33 & 40 & 30 & 20 & 14 & 12\\
(263169, 513) & 19 & 35 & 39 & 28 & 19 & 14 & 11\\
(1050625, 1025) & 22 & 34 & 37 & 27 & 19 & 14 & 11\\
(4198401, 2049) & 24 & 34 & 34 & 25 & 17 & 12 & 9\\
(8392609, 2897) & 25 & 32 & 32 & 24 & 16 & 11 & 8\\
(11068929, 3327) & 25 & 32 & 32 & 25 & 16 & 13 & 11\\
\hline
\end{tabular}
}
\end{table}
%
\begin{table}[ht]
  \caption{Iteration counts with the $Q$-cap preconditioned system (top) and $W$-cap 
  preconditioned system (bottom) for different values of parameter $\epsilon$. 
  \textit{Non-uniform} mesh.
}
\label{tab:iter_unif}
\footnotesize{
\begin{tabular}{l|ccccccc}
\hline
($n$, $m$)\textbackslash $\epsilon$ & $10^{-3}$ & $10^{-2}$ & $10^{-1}$ & $10^{0}$ & $10^{1}$ & $10^{2}$ & $10^{3}$\\
\hline
(87260, 422) & 26 & 40 & 42 & 36 & 32 & 29 & 24\\
(348555, 841) & 28 & 41 & 41 & 35 & 32 & 29 & 24\\
(1389644, 1681) & 32 & 42 & 40 & 36 & 33 & 28 & 23\\
(5547222, 3360) & 35 & 42 & 40 & 36 & 31 & 26 & 22\\
(10031652, 4514) & 35 & 40 & 38 & 34 & 31 & 26 & 21\\
\hline
\hline
(87260, 422) & 22 & 37 & 44 & 34 & 24 & 20 & 17\\
(348555, 841) & 23 & 37 & 42 & 33 & 23 & 18 & 15\\
(1389644, 1681) & 27 & 38 & 39 & 32 & 22 & 18 & 17\\
(5547222, 3360) & 28 & 36 & 37 & 30 & 22 & 19 & 16\\
(10031652, 4514) & 28 & 35 & 36 & 30 & 22 & 19 & 17\\
\hline
\end{tabular}
}
\end{table}

\subsection*{Computation Costs} We shall now address the second point of the 
reviewers' comments. For simplicity we let $\epsilon=1$. In case of the $Q$-cap 
preconditioner the operator to be assembled takes the form
$\text{diag}(\text{AMG}(A_2), A^{-1}, H^{-1})$, 
where $A_2$, $A$ are the discretized 2$d$, 1$d$ Laplacians and $H$ is the matrix 
assembled from the generalized eigenvalue problem(GEVP)
%
\begin{equation}\label{eq:gevp}
  Ax=\lambda M x
\end{equation}
%
with $M$ the one dimensional mass matrix. The $W$-cap preconditioner is then 
$\text{diag}(\text{AMG}(A_2+\dual{T}AT)), A^{-1}, C)$  where $T$ is the 2$d$-1$d$ 
trace/restriction and matrix $C=M^{-1}AM^{-1}$. 

Clearly, the most costly operations required by the $Q$-cap preconditioner are
computation of AMG and solving GEVP \eqref{eq:gevp}. Unlike
$Q$-cap, the $W$-cap preconditioner requires AMG on a new operator
$A_2+\dual{T}AT$, which is not computed as part of the system(left hand side). 
For completeness we will monitor costs of the assembly (ADD). We remark that in our
implementation the product term is not assembled with the dedicated PETSc
routine \texttt{MatPtAP} but with two matrix-matrix multiplications. This is
potentially suboptimal. Finally we shall keep track of the total cpu time
required for convergence of preconditioned MinRes method.

\begin{table}[h]
  \caption{Timings of elements of construction of the $Q$, $W$-cap
  preconditioners on \textit{uniform} mesh. The numbers in the brackets show 
  estimated complexity of computing quantitiy $v$ at $i$-th row,
  $r_i=\sfrac{\log{v_i}-\log{v_{i-1}}}{\log{m_i}-\log{m_{i-1}}}$. Final row is
  the least squares fit of the reported data(the last row of AMG, ADD
  timings is ignored) giving complexity $v=\mathcal{O}(m^r)$.
}
\label{tab:timings_unif}
\footnotesize{
\begin{tabular}{c|lll|lll}
\hline
 & \multicolumn{3}{c|}{$Q$-cap} & \multicolumn{3}{c}{$W$-cap}\\
\hline
  $m$ & AMG$\left[s\right]$ & GEVP$\left[s\right]$ & MinRes$\left[s\right]$ &
        AMG$\left[s\right]$ & ADD$\left[s\right]$  & MinRes$\left[s\right]$ \\
\hline
  257  & 0.075(1.98)  & 0.014(1.81)  &  0.579(1.69)  & 0.078(1.94)  & 0.012(1.85)   & 0.514(1.73)  \\
  513  & 0.299(2.01)  & 0.066(2.27)  &  2.286(1.99)  & 0.309(1.99)  & 0.047(1.94)   & 2.019(1.98)  \\
  1025 & 1.201(2.01)  & 0.477(2.87)  &  8.032(1.82)  & 1.228(1.99)  & 0.185(1.99)   & 7.909(1.97)  \\
  2049 & 4.983(2.05)  & 3.311(2.80)  &  30.814(1.94) & 4.930(2.01)  & 0.738(2.00)   & 30.309(1.94) \\
  2897 & 9.686(1.92)  & 8.384(2.68)  &  62.666(2.05) & 10.644(2.22) & 1.463(1.98)   & 59.132(1.93) \\
  3327 & 15.940(3.60) & 12.253(2.74) &  84.431(2.15) & 15.650(2.79) & 11.171(14.69) & 82.132(2.37) \\
\hline
% Qamg 2.02 Qeig 2.70 Vamg 2.02 Vadd 1.98 3761 8886110
  & (2.02) & (2.70) & (1.92) &
    (2.02) & (1.98) & (1.96) \\
\hline
\end{tabular}
}
\end{table}
%
The observed timings are reported in tables \ref{tab:timings_unif},
\ref{tab:timings_nonunif}. We remark that with both \textit{uniform} and \textit{non-uniform} 
mesh the numbers reported for AMG and ADD on the final discretizations deviate 
from the trend set by the predecessors. This is likely because SWAP memory was 
required to complete the operations and the cases should therefore be omitted 
from the discussion. In the remaining cases we observe that AMG construction 
scales quadratically with $m$ and the inclussion of the trace term has little effect 
on the construction time. Moreover assembly of $A_2+\dual{T}AT$ has negligible 
costs in comparison to AMG.

For smaller problem the $W$-cap preconditioner is about as expansive to construct 
as the $Q$-cap preconditioner. For larger problems, requiring order of thousand
eigenvalues, the contribution of GEVP solve time to the total cost becomes
evident. As a result $Q$-cap becomes about twice as expensive to construct as the 
$W$-cap. We remark that the solution times with both preconditioners are
practically identical for \textit{uniform} mesh. On the other mesh $W$-cap
preconditioner requires fewer iterations and becomes faster as the size of the 
problem grows. Moreover the solution time dominates the construction time.

In our results, GEVP takes always less time than AMG. However, based on mesh, 
the employed solver, \texttt{LAPACK.SYGVD}, appears to be $\mathcal{O}(m^{2.7})$
or $\mathcal{O}(m^{2.8})$ in complexity and thus with increasing $m$, solving 
the eigenvalue problem might dominate the construction of the $Q$-cap preconditioner.
Using the least squares fit\footnote{Note that AMG, ADD do not include the last
discretizations effected by the swapping into considerations. For GEVP all the
reported timings are included.} we can estimate the size of the problem where the
cost of GEVP matches that of AMG. On the \textit{uniform} mesh, that moment is
projected to happen at $(n, m)=(8886110, 3761)$. On the other hand, the
unstructured discretization results in $(24154952, 7527)$. 

Based on the observed timings, we conclude that $W$-cap preconditioner is more
practical than the $Q$-cap preconditioner. However, $Q$-cap preconditioner is
certainly \textit{not} impractical. One can of course imagine conditions where
the size of the one dimensional problem grows faster than reported here, e.g.
mesh refined heavily towards the 1$d$ domain, or, 1$d$ domain being a space
filling curve, but for many applications the $Q$-cap can be an efficient 
preconditioner.
%
\begin{table}[ht]
  \caption{Timings of elements of construction of the $Q$, $W$-cap
  preconditioners on \textit{non-uniform} mesh. The numbers in the brackets show 
  estimated complexity of computing quantitiy $v$ at $i$-th row,
  $r_i=\sfrac{\log{v_i}-\log{v_{i-1}}}{\log{m_i}-\log{m_{i-1}}}$. Final row is
  the least squares fit of the reported data(the last row of AMG, ADD
  timings is ignored) giving complexity $v=\mathcal{O}(m^r)$.}
\label{tab:timings_nonunif}
\footnotesize{
\begin{tabular}{c|lll|lll}
\hline
 & \multicolumn{3}{c|}{$Q$-cap} & \multicolumn{3}{c}{$W$-cap}\\
\hline
$m$ & AMG$\left[s\right]$ & GEVP$\left[s\right]$ & MinRes$\left[s\right]$ &
      AMG$\left[s\right]$ & ADD$\left[s\right]$  & MinRes$\left[s\right]$ \\
\hline
212  & 0.046(2.03)  & 0.005(1.62)  & 0.280(1.27)   & 0.049(2.10)  & 0.005(1.86) & 0.279(1.45)   \\
422  & 0.188(2.04)  & 0.018(2.05)  & 1.082(1.96)   & 0.189(1.96)  & 0.018(1.75) & 0.978(1.82)   \\
841  & 0.783(2.07)  & 0.099(2.43)  & 4.507(2.07)   & 0.785(2.07)  & 0.066(1.92) & 4.127(2.09)   \\
1681 & 3.191(2.03)  & 1.001(3.35)  & 18.861(2.07)  & 3.190(2.02)  & 0.257(1.96) & 16.807(2.03)  \\
3360 & 13.004(2.03) & 8.004(3.00)  & 78.847(2.07)  & 13.220(2.05) & 0.986(1.94) & 68.301(2.02)  \\
4514 & 25.465(2.28) & 18.824(2.90) & 144.015(2.04) & 30.406(2.82) & 2.178(2.69) & 129.755(2.17) \\
\hline
% Qamg 2.04 Qeig 2.80 Vamg 2.03 Vadd 1.90 7527 24154952
  &  (2.04) & (2.80) & (2.05) &
     (2.03) & (1.90) & (2.00)  \\
\hline
\end{tabular}
}
\end{table}

% Only symmetry - what about tridiagonaly - there are n^2, n*log(n) algorithm
In the previous results the generalized eigenvalue problem \eqref{eq:gevp} was 
solved with an algorithm of nearly cubic complexity which only took into account 
the symmetry of matrices of $A$, $M$. However, as we use CG$_1$ discretization, the matrices
have more structure. In fact, for \textit{uniform} mesh, or any geometry where
the 1$d$ domain has no branching, the matrices are tridiagonal and the $Q$-cap 
construction could be made more efficient with an algorithm which would exploit 
fully the structure of the eigenvalue problem. An $\mathcal{O}(m^2)$\footnote{This 
scaling is established for rather small problems $m<1000$.}. of this kind is given 
in \cite{gevp_s3d}. Unfortunately it is not implemented in available linear packages 
and we do not have resources to implement it ourselves. Therefore we only comment 
that iff 1$d$ domain \textit{has no branching} \cite{gevp_s3d} is potentially a mean 
to make GEVP scale like AMG.

% No branching
Let us assume that the 1$d$ domain is free of bifurcations. There are routines already 
implemented in LAPACK for dealing with eigenvalue problems (EVP) with symmetric 
tridiagonal matrices, i.e. $Ax=\lambda x, A=\dual{A}$, which enjoy nearly quadratic 
scaling \cite{demmel}. Therefore, a possible path to a faster $Q$-cap preconditioner 
is to transform GEVP into EVP with a symmetric tridiagonal matrix. Naturally, such a 
transformation is only meaningful if the resulting modified $Q$-cap preconditioner 
remains a good preconditioner for our coupled problem.

\section*{Efficiency}Let us first assume that were are able to
transform GEVP and see how much performance can be gained this way. Table
\ref{tab:evp} shows cpu time required to computed $m$ sized eigenvalue problem
$Ax=\lambda x$ in comparison to $m$ sized generalized eigenvalue problem
$Ax=\lambda M x$. Both systems are assembled on a \textit{uniform} mesh. In the
later case we use, as before, LAPACK's \texttt{SYGVD} routine while the EVP is
solved with \texttt{LAPACK.STEGR} routine which implements the method of
Multiple Relatively Robust Representations \cite{mmmr} - a nearly
$\mathcal{O}(m^2)$ algorithm. We observe that the method scales as $m^{2.34}$
which is close to what \cite{demmel} reported for a jungle of matrices with size
$m<10^4$. It is evident that there is something to gain in efficiency by considering
possible transformation of GEVP.
%
% Comment on complexity of tridiag. Show the numbers GEVP vs. EVP tridiag.
%
\begin{table}
\caption{Comparison of timings for transformed EVP\eqref{eq:evp} and 
  GEVP\eqref{eq:gevp}. GEVP is solved by \texttt{LAPACK.SYGVD}. (Left) The
  symmetric tridiagonal EVP is solved with LAPACK's \texttt{STEGR}. (Right)
  The symmetric EVP is solved with LAPACK's \texttt{SYEVR}. Both results 
  are obtained with Intel Core i5-4570S cpu clocking at 2.9 Ghz}
\label{tab:evp}
\begin{subtable}{0.48\textwidth}
  \centering
  \footnotesize{
  \begin{tabular}{l|ll}
  \hline
    m & EVP$\left[s\right]$ & GEVP$\left[s\right]$\\
  \hline
  1025 & 0.080(1.90) & 0.396(2.56)\\
  2049 & 0.312(1.96) & 2.631(2.73)\\
  4097 & 1.363(2.13) & 18.846(2.84)\\
  8193 & 7.717(2.50) & 122.875(2.71)\\
  16385 & 53.001(2.78) & 876.484(2.83)\\
  \hline
      & (2.34) & (2.78)\\
  \hline
  \end{tabular}
  }
\end{subtable}
%
\begin{subtable}{0.48\textwidth}
  \centering
  \footnotesize{
  \begin{tabular}{l|ll}
  \hline
    m & EVP$\left[s\right]$ & GEVP$\left[s\right]$\\
  \hline
  422 & 0.031(1.47) & 0.042(2.43)\\
  841 & 0.133(2.13) & 0.178(2.08)\\
  1681 & 0.823(2.63) & 1.294(2.86)\\
  3360 & 6.224(2.92) & 9.631(2.90)\\
  4514 & 16.275(3.26) & 21.886(2.78)\\
  \hline
    & (2.66) & (2.69)\\
  \hline
  \end{tabular}
  }
\end{subtable}
\end{table}

% Define the approximations
Matrix $H$, which is the ultimate diagonal block in the matrix representation of
the $Q$-cap preconditioner, is based on eigenpairs $(\lambda, u)$ such that 
$Au=\lambda M u$. In particular, matrices $H_s=M(U\Lambda^s \dual{U})M$, where
$AU=MU\Lambda$, are used in its definition. Let us define $M_l$ as the lumped
mass matrix and cosequently matrices $U_l, \Lambda_l$ which are such that
$AU_l=M_l U_l\Lambda$. Then we shall define an approximation of $H_s$ as
$\hat{H}_s=M(U_l\Lambda^s_l\dual{U})M$. Substituting for $H_s$ in the definition
of $H$ and the $Q$-cap we obtain a modified operator which shall be termed 
$\hat{Q}$-cap preconditioner.
% On computation
Note that $\Lambda_l, U_l$ can by obtained by transforming GEVP into an EVP with 
with a symmetric tridiagonal matrix
\begin{equation}\label{eq:evp}
  M_l^{-1/2}A M_l^{-1/2} V=V\Lambda_l.
\end{equation}
We remark that that the \eqref{eq:evp} and the original GEVP have the same
eigenvalues but the eigenvectors must be transformed as $U_l=M_l^{-1/2} V$.

In case the mesh has bifurcations $M_l^{-1/2}A M_l^{-1/2}$ is no longer 
triangular. Still, either in form \eqref{eq:evp} or the form of a
generalized eigenvalue problem $Au=\lambda M_l u$, the problem is cheaper to
solve than \eqref{eq:gevp}. Among other reasons, there is no need to (Cholesky) 
factor $M$. The savings are shown in table \ref{tab:evp}.

Performance of the approximation is summarized in table \ref{tab:hatQcap} which
reports condition numbers of the $\hat{Q}$-cap preconditioned system for both
types of meshes. Condition numbers are bounded. Moreover they are smaller than
those of the $Q$-cap preconditioner.
%
\begin{table}[hb]
  \caption{Condition numbers of $\hat{Q}$-cap preconditioned system for different 
  values of parameter $\epsilon$. (Top) \textit{Uniform} mesh.
  (Bottom) \textit{non-uniform} mesh.
}
\label{tab:hatQcap}
\footnotesize{
\begin{tabular}{l|ccccccc}
\hline
($n$, $m$)\textbackslash $\epsilon$ & $10^{-3}$ & $10^{-2}$ & $10^{-1}$ & $10^{0}$ & $10^{1}$ & $10^{2}$ & $10^{3}$\\
\hline
(25, 5) & 2.626 & 2.697 & 3.216 & 4.357 & 4.764 & 4.817 & 4.823\\
(81, 9) & 2.636 & 2.788 & 3.677 & 4.704 & 4.846 & 4.872 & 4.875\\
(289, 17) & 2.655 & 2.951 & 4.208 & 4.904 & 4.923 & 4.930 & 4.930\\
(1089, 33) & 2.693 & 3.228 & 4.707 & 5.015 & 4.950 & 4.946 & 4.946\\
(4225, 65) & 2.766 & 3.645 & 5.092 & 5.075 & 4.960 & 4.953 & 4.952\\
(16641, 129) & 2.901 & 4.172 & 5.343 & 5.106 & 4.964 & 4.955 & 4.954\\
(66049, 257) & 3.138 & 4.708 & 5.490 & 5.121 & 4.966 & 4.956 & 4.955\\
\hline
\hline
(1466, 55) & 2.689 & 3.182 & 4.468 & 4.834 & 4.852 & 4.855 & 4.855\\
(5584, 107) & 2.756 & 3.525 & 4.693 & 4.808 & 4.801 & 4.801 & 4.801\\
(21905, 212) & 2.871 & 3.945 & 4.931 & 4.902 & 4.884 & 4.883 & 4.883\\
(87260, 422) & 3.082 & 4.398 & 5.033 & 4.884 & 4.855 & 4.853 & 4.853\\
\hline
\end{tabular}
}
\end{table}



\section*{Todo}
Address points (iii) by researching complexity of other available methods. 
Point (iv) vaguely ...

Some questions: (1) Do we include efficiency into the paper? (2) Should all the 
computations be performed on both meshes and the results included in the response 
to reviewers. Note that on \textit{non-uniform} we do not have an analutical 
solution to test against.

\bibliographystyle{plain}
\bibliography{report}

\end{document}
